### 2019-06-18 2-Chapters/1-Chapter/chapter1.tex
J'ai hâte de finir ! Pas le temps d'aller voir Xtof désoooolé

\TODOL{Mardi : je dois encore relire le 1.1 pour les fautes d'orthographe (et les éventuels erreurs historiques) !}
\TODOL{Mardi : je dois encore terminer le 1.2 et être plus concis ?}
\TODOL{Je dois écrire la fin du 1.3 en max 2 pages : j'ai déjà le plan, je dois développer}

@@

As explained above, the model of Chapter~\ref{chapter:4} was found intractable to analyze because we consider an IoT network with many end-devices, all following random activation patterns.
Generalizing to different activation probabilities would lead to a model even harder to analyze, and enforcing at most $M \leq K$ devices is not really realistic for IoT networks, but leads to the model of Chapter~\ref{chapter:5}.
%
On the first hand, if the activation pattern of all devices could be fixed, for instance based on a centralized affectation of the devices to different time slots, then the model of multi-player bandit from Chapter~\ref{chapter:5} can be used to let the devices learn an optimal orthogonal affectation of $M \leq K$ devices in the $K$ channels.
However, it is hard to argue that this hypothesis of a centralized time schedule for the end-devices can be realistic, because we study the case of decentralized learning for OSA and IoT precisely in order to avoid any central control of the devices by the base station, as we explained above.
%
On the other hand, FIXME explain why is it interesting to study piece-wise stationary problems from the point-of-view of one player...

@@

@@

\TODOL{Je suis content de la suite de l'intro : aperçu des contributions, plans de thèse, liste des publications}

@@

    \item
    We also present the piece-wise stationary MAB model, in Chapter~\ref{chapter:6}, and a detailed literature review of the research on non stationary MAB \cite{Besson2019GLRT,Besson2019Gretsi}.
    Following two recent works, we propose a new actively adaptive algorithm for the piece-wise stationary problem, \GLRklUCB, that achieves state-of-the-art performance.
    % - Literature review on non stationary models and algorithms, state-of-the-art for piece-wise stationary with our algorithm, GLR test + klUCB

@@

\begin{itemize}
\item
    \emph{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation},
    by Christophe Moy \& \textbf{Lilian Besson}.
    1st International ISIoT workshop,
    % \footnote{~See \href{https://sites.google.com/view/ISIoT2019}{\texttt{sites.google.com/view/ISIoT2019}}},
    at \emph{Conference on Distributed Computing in Sensor Systems},
    % \footnote{~IEEE DCOSS 2019, see \href{http://2019.dcoss.org}{\texttt{2019.dcoss.org}}},
    Santorini, Greece, May 2019.
    % \href{https://HAL.Inria.fr/hal-02144465}{\texttt{HAL.Inria.fr/hal-02144465}}.
    See Section~\ref{sec:4:gnuradio}.
    \cite{MoyBesson2019}

@@

\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann,
    February $2019$.
    See Chapter~\ref{chapter:6}.
    Preprint at \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019GLRT}

>>>>

\TODOL{Mardi soir : je dois encore relire le 1.1 pour les fautes d'orthographe (et les éventuels erreurs historiques) !}
\TODOL{Mardi soir : je dois encore améliorer le 1.2 et être plus concis ?}
\TODOL{Mardi soir : je dois relire la fin du 1.3, et terminer le dernier point}

@@

As explained above, the model of Chapter~\ref{chapter:4} was found intractable to analyze because we consider an IoT network with many end-devices, all following random activation patterns.
Generalizing to different activation probabilities would lead to a model even harder to analyze, and enforcing at most $M \leq K$ devices is not really realistic for IoT networks, but leads to the model of Chapter~\ref{chapter:5}.
%
On the first hand, if the activation pattern of all devices could be fixed, for instance based on a centralized affectation of the devices to different time slots, then the model of multi-player bandit from Chapter~\ref{chapter:5} can be used to let the devices learn an optimal orthogonal affectation of $M \leq K$ devices in the $K$ channels.
However, it is hard to argue that this hypothesis of a centralized time schedule for the end-devices can be realistic, because we study the case of decentralized learning for OSA and IoT precisely in order to avoid any central control of the devices by the base station, as we explained above.
%
On the other hand,
FIXME explain why is it interesting to study piece-wise stationary problems from the point-of-view of one player...
\TODOL{Mardi soir je dois encore expliquer ça !}

@@

\TODOL{Mardi soir je peux mieux expliquer, là je suis long et chiant je trouve}

@@

% \TODOL{Je suis content de la suite de l'intro : aperçu des contributions, plans de thèse, liste des publications}

@@

    \item
    We also present the piece-wise stationary MAB model, in Chapter~\ref{chapter:6}, and a detailed literature review of the research on non-stationary MAB \cite{Besson2019GLRT,Besson2019Gretsi}.
    Following two recent works, we propose a new actively adaptive algorithm for the piece-wise stationary problem, \GLRklUCB, that achieves state-of-the-art performance.
    % - Literature review on non stationary models and algorithms, state-of-the-art for piece-wise stationary with our algorithm, GLR test + klUCB

@@

\begin{itemize}
\item
    \emph{Decentralized Spectrum Learning for IoT Wireless Networks Collision Mitigation},
    by Christophe Moy \& \textbf{Lilian Besson}.
    1st International ISIoT workshop,
    % \footnote{~See \href{https://sites.google.com/view/ISIoT2019}{\texttt{sites.google.com/view/ISIoT2019}}},
    at \emph{Conference on Distributed Computing in Sensor Systems},
    % \footnote{~IEEE DCOSS 2019, see \href{http://2019.dcoss.org}{\texttt{2019.dcoss.org}}},
    Santorini, Greece, May 2019.
    % \href{https://HAL.Inria.fr/hal-02144465}{\texttt{HAL.Inria.fr/hal-02144465}}.
    See Section~\ref{sec:4:gnuradio}.
    \cite{MoyBesson2019}
    Note that we are already working on an extended version that will be submitted to a journal in July $2019$.

@@

\item
    \emph{The Generalized Likelihood Ratio Test meets klUCB: an Improved Algorithm for Piece-Wise Non-Stationary Bandits},
    by \textbf{Lilian Besson} \& Emilie Kaufmann,
    February $2019$.
    See Chapter~\ref{chapter:6}.
    Preprint at \href{https://HAL.Inria.fr/hal-02006471}{\texttt{HAL.Inria.fr/hal-02006471}}.
    \cite{Besson2019GLRT}
    Note that we are already working on an extended version that will be submitted to a journal in autumn $2019$.
